Bow shocks, bow waves, and dust waves. III. Diagnostics

### 2019-03-26 papers/Papers1234/bs-bw-dw-03.tex
Finish everything except summary on Paper III

@@

\section{Notes on particular sources}
\label{sec:notes-part-sourc}

\subsection{Source~380, HD~53367, V750~Mon}
\label{sec:hd-53367-v750}

This is a Herbig Be star with spectral type B0V--B0III and mass 12 to
\SI{15}{M_\odot}, which shows long-scale irregular photometric
variability \citep{Tjin-A-Djie:2001a, Pogodin:2006a} together with
cyclic radial velocity variations, which are interpreted as an
eccentric binary with a \SI{5}{M_\odot} pre-main-sequence companion.
It is located outside the solar circle and, although it was originally
classified as part of the CMa OB association at about \SI{1}{kpc}
\citep{Tjin-A-Djie:2001a}, more recent estimates put it much closer.
K18 assume a distance of \SI{260}{pc}, based on Hipparcos measurements
\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
puts it closer still at \SI{140 \pm 30}{pc}.\footnote{%
  Median and 90\% confidence interval, estimated from Bayesian
  inference using an exponential density distribution with scale
  length of \SI{1350}{pc} as a prior (see
  \url{https://github.com/agabrown/astrometry-inference-tutorials/}). }

@@

\subsection{Source 407, HD~93249}
\label{sec:source-407}

TODO

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/cygnus-bows-midir-combo}
  \caption{Two bows in Cygnus}
  \label{fig:cygnus-bows}
\end{figure}

\subsection{Source 342}
\label{sec:source-342}

Source~342 is anomalous in both methods. Has high mass loss for low luminosity.

\subsection{Source 344}
\label{sec:source-344}

This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?

>>>>

We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
diagram, for analyzing observations of stellar bow shocks around OB
stars, which allows discrimination between radiation-supported and
wind-supported bows.  Our principal results are as follows:
\begin{enumerate}[1.]
\item The UV optical depth \(\tau\) of the bow shell can be estimated
  from the observed infrared shell luminosity \(L\IR\) and stellar
  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\).
\item The shell momentum efficiency \(\eta\shell\), which is the
  fraction of stellar radiative momentum that is transferred to the
  shell either directly or indirectly (via stellar wind), can be
  estimated from \(\tau\) and the observed shell radius \(R_0\), after
  making some auxiliary assumptions about the physical conditions in
  the shell.
\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
  discriminate between three regimes (see Paper~I): wind-supported bow
  shocks (\(\eta\shell \gg \tau\)), radiation-supported bow waves
  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
  (\(\eta\shell \sim \tau > 1\)).
\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a fourth
  dust-wave regime where gas--grain collisional coupling may break
  down (see Paper~II).
\item 
\end{enumerate}

@@

% \section{Notes on particular sources}

\section{The Herbig Be star V750~Mon}
\label{sec:notes-part-sourc}
\label{sec:hd-53367-v750}

K18 source~380 (HD~53367, V750~Mon) is a Herbig Be star with spectral
type B0V--B0III and mass 12 to \SI{15}{M_\odot}, which shows
long-scale irregular photometric variability \citep{Tjin-A-Djie:2001a,
  Pogodin:2006a} together with cyclic radial velocity variations,
which are interpreted as an eccentric binary with a \SI{5}{M_\odot}
pre-main-sequence companion.  It is located outside the solar circle
and, although it was originally classified as part of the CMa OB
association at about \SI{1}{kpc} \citep{Tjin-A-Djie:2001a}, more
recent estimates put it much closer.  K18 assume a distance of
\SI{260}{pc}, based on Hipparcos measurements
\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
puts it closer still at \SI{140 \pm 30}{pc}.  This is the median and
90\% confidence interval, estimated from Bayesian
inference\footnote{\url{https://github.com/agabrown/astrometry-inference-tutorials/}.}
using an exponential density distribution with scale length of
\SI{1350}{pc} as a prior.

@@

% \subsection{Source 407, HD~93249}
% \label{sec:source-407}

% TODO

% \subsection{Source 342}
% \label{sec:source-342}

% Source~342 is anomalous in both methods. Has high mass loss for low luminosity.

% \subsection{Source 344}
% \label{sec:source-344}

% This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?

### 2019-03-26 papers/Papers1234/sec-observational-diagnostics.tex
Finish everything except summary on Paper III

@@

\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
\label{sec:mass-loss-determ}
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Wind mass-loss rates as a function of stellar luminosity,
    derived from (a)~our trapped energy/momentum method and (b)~the
    grain emissivity method of \citet{Kobulnicky:2018a}, with
    corrections as described in our \S~\ref{app:bow-shock-data}.
    Circle symbols show the sources from K18, colored according to the
    stellar effective temperature (see key at far right). In panel a,
    squares show two of our additional sources
    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
    given for sources that lie close to the radiation-supported line
    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
    symbols and downward-pointing arrows.  Sources that lie less than
    a factor of three above the line have enhanced downward
    uncertainties and are also shown by slightly fainter symbols.  For
    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
    luminosities of the triple OB system Aa, Ab, and B
    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
    the luminosity of only the most massive component Aa.  Lines show
    the predictions of stellar wind models: red lines are the commonly
    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
    (dashed), and supergiants (dotted), while black lines show
    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
    mass-loss measurements from NUV lines for weak-wind O~dwarfs
    \citep{Marcolino:2009a}, while the green plus symbol shows the
    measurement from infrared H recombination lines for \(\sigma\)~Ori
    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
    to observational uncertainties (lower right) and assumed shell
    parameters (upper left).}
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}

@@

\textit{Write about sigma Ori}

@@

\newcommand\LOS{\ensuremath{_{\text{los}}}}

@@

\subsection{Why do the two mass-loss methods differ?}
\label{sec:underst-diff-betw}

@@

Although we have seen (Fig.~\ref{fig:mass-loss-comparison}) that the
mass-loss discrepancy increases with \(R_0\), it is hard to understand
why the physical size per~se might cause this.  We have therefore
looked at the correlations between all of the observed and derived
quantities, showing some of the more interesting results in
Figure~\ref{fig:correlations}.  Each row of plots shows the dependence
(\(y\) axis) of the two different derived mass-loss rates, and their
ratio, on different parameters (\(x\) axis) of the star (leftmost four
columns) and bow shell (remaining six columns).  The most significant
correlations are marked in red with the value of the Pearson
correlation coefficient, \(r\) (calculated after taking the log of all
quantities).  The values shown with dark text have \(r^2 > 0.5\),
which means that at least 50\% of the variance in the \(y\) quantity
is ``explained'' by the variance in the \(x\) quantity (although this
cannot necessarily be taken to imply causation in either
direction). For some correlations, we also mark the linear regression
slope, \(m\).  Since we are working in logarithmic space, this is
equal to the power index in the relation \(y \propto x^m\).  Some
selected weaker correlations are also shown (fainter text).

@@

Out of the three quantities, \(R_0\), \(\ell/R_0\), and \(U\) (which
are highly correlated between themselves) we will concentrate on the
relative chord length \(\ell/R_0\) as the most likely culprit for the
discrepancy between the two mass-loss estimates.  This is because it
contains observational information that is used in the K18 method
(step K\ref{K2} of \S~\ref{app:bow-shock-data}), but is \textit{not
  used} in the \(\tau\)--\(\eta\shell\) method.  The closest
equivalent of \(\ell\) in our method is the shell thickness,
\(h\shell\), which enters in step~P\ref{P2} of
\S~\ref{sec:energy-trapp-vers}, but crucially we use a fixed fraction
of the bow radius, \(h\shell / R_0 = 0.25\), rather than basing it on
any observations.  In principle, we could derive \(h\shell\) from
\(\ell\) if we knew the radius of curvature of the shell,
\(R_{\text{c}}\), or equivalently the planitude:
\(\Pi = R_{\text{c}} / R_0\)\citep{Tarango-Yong:2018a}.  The idealized
geometry is illustrated in the inset to Figure~\ref{fig:H-versus-ell},
from which we find
\begin{equation}
  \label{eq:h-R0}
  \frac{h\shell}{R_0} = \frac{1}{8\Pi} \left(\frac{\ell}{R_0}\right)^2 \ .
\end{equation}
This is plotted in Figure~\ref{fig:H-versus-ell} for planitudes of
\(\Pi = 1.8 \pm 0.9\), which are typical of OB star bows (this will be
shown in detail in the upcoming Paper~IV).  Also shown in the figure
are the individual relative chord lengths for the K18 sources (rug
plot at top).  Although the mean value of \(\ell/R_0 \approx 1.8\)
corresponds closely to the \(h\shell/R_0 = 0.25\) that we have used,
the sources with \(\ell/R_0 < 1\) are predicted to have thinner shells
with \(h\shell/R_0 < 0.1\).  The four sources with the lowest values
of \(\ell/R_0\) are labeled on the figure (369, 339, 382, 344) and
these are precisely those sources that show the largest discrepancy
between the two mass loss methods
(Fig.~\ref{fig:mass-loss-comparison}).  Using a smaller value of
\(h\shell\) would increase \(\eta\shell\) (eq.~[\ref{eq:eta-shell}])
and hence \(\dot{M}\) (eq.~[\ref{eq:mdot-tau-eta}]), thereby reducing
the discrepancy between the two methods.

@@

K18 source~342 is the only source that shows a significant discrepancy
\textit{above} the theoretical mass-loss rate predictions.  This is
bow shock candidate~2 in a survey of mid-infrared arcs in Cygnus~X
\citep{Kobulnicky:2010a}, and is referred to as KGK2010~2 in
subsequent works.  For its early~B spectral type,
\(\dot{M} \approx \SI{3e-9}{M_\odot.yr^{-1}}\) is expected, whereas
the derived values from both mass-loss methods (panels a and b of
Fig.~\ref{fig:mass-loss-vs-luminosity}) are about 10 times larger.
This fact was already noted in K18, who suggested that the grain
emissivity models may not be appropriate for this object.  We propose
instead that the shell may be predominantly neutral instead of
ionized, which might help explain other peculiar aspects of the
source.  Figure~\ref{fig:cygnus-bows} shows infrared images of the
field containing both sources~342 and 341.  The field is located in
the Cygnus~X North region, between the DR~20 and DR~21 star forming
regions, about \SI{17}{pc} north of the center of the Cygnus OB2
association \citep[e.g.,][]{Schneider:2016a}.  It can be seen that the
two bow shocks have very contrasting morphologies and spectra.
Source~341 has a semi-circular shape, a very diffuse outer boundary,
and is only prominent between wavelengths of \SI{12}{\um} and
\SI{24}{\um}.  These characteristics are typical of many optically
thin bows seen in fully ionized gas, such as the Ney--Allen nebula
around \thD{} \citetext{compare the bow shape in Fig.~3a of
  \citealp{Smith:2005a}}, source~406 \citetext{HD~92607, which is
  ERO~36 in Carina, \citealp{Sexton:2015b}}, and the central star of
RCW~120 \citetext{not included in current samples, but see
  \citealp{Mackey:2015a, Mackey:2016a}}.  Source~342, on the other
hand, has a more parabolic shape, a sharply defined arc, and emits
strongly at all wavelengths from \SI{3.6}{\um} to \SI{150}{\um}
\citetext{see also Fig.~13 of \citealp{Kobulnicky:2010a}}.  The
parabolic arc shape and the broad SED are both reminiscent of LP~Ori
(more details on the Orion Nebula bows will be provide in Paper~VI),
and another bow that bears some similarities is Carina's Sickle object
\citetext{ERO~21 \citealp{Sexton:2015b}, see also
  \citealp{Ngoumou:2013a}}.  Note also the second outer arc in this
source, which emits primarily at \SI{5.8}{\um} and \SI{7.9}{\um} and
appears similar to the double-bow structure seen in IRAS~03063+5735
\citep{Kobulnicky:2012a}.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Wind mass-loss rates as a function of stellar luminosity,
    derived from (a)~our trapped energy/momentum method and (b)~the
    grain emissivity method of \citet{Kobulnicky:2018a}, with
    corrections as described in our \S~\ref{app:bow-shock-data}.
    Circle symbols show the sources from K18, colored according to the
    stellar effective temperature (see key at far right). In panel a,
    squares show two of our additional sources
    (Tab.~\ref{tab:observations}). Upper limits to the mass loss are
    given for sources that lie close to the radiation-supported line
    in Fig.~\ref{fig:All-sources-eta-tau}, represented by faint
    symbols and downward-pointing arrows.  Sources that lie less than
    a factor of three above the line have enhanced downward
    uncertainties and are also shown by slightly fainter symbols.  For
    \(\sigma\)~Ori, the large symbol corresponds to the sum of the
    luminosities of the triple OB system Aa, Ab, and B
    \citep{Simon-Diaz:2015a}, while the small symbol corresponds to
    the luminosity of only the most massive component Aa.  Lines show
    the predictions of stellar wind models: red lines are the commonly
    used recipes from \citet{Vink:2000a} for dwarfs (solid), giants
    (dashed), and supergiants (dotted), while black lines show
    eq.~(11) of \citet{Krticka:2017a} for O~stars (solid) and models
    of \citet{Krticka:2014a} for B stars.  Orange plus symbols show
    mass-loss measurements from NUV lines for weak-wind O~dwarfs
    \citep{Marcolino:2009a}, while the green plus symbol shows the
    measurement from infrared H recombination lines for \(\sigma\)~Ori
    \citep{Najarro:2011a}.  Boxes show the sensitivity of the results
    to observational uncertainties (lower right) and assumed shell
    parameters (upper left).}
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}

@@

\subsection{Mass loss determination from the \boldmath \(\tau\)--\(\eta\shell\) diagram}
\label{sec:mass-loss-determ}

@@

@@

@@

In this section we discuss various issues related to our results,
beginning in \S~\ref{sec:evolution-grain-size} with a consideration of
how the optical properties of the grain population in bow shocks might
be affected by the extreme radiation environment.  This is followed by
examination of various sub-groups of sources that are unusual in some
way: those where the two mass-loss methods give discrepant results
(\S~\ref{sec:underst-diff-betw}), those that may be
radiation-supported (\S~\ref{sec:comm-prop-cand}), and one source that
shows a very large apparent mass-loss rate for its luminosity
(\S~\ref{sec:anomalous-b-star}).

\subsection{Why do results of the two mass-loss methods differ?}
\label{sec:underst-diff-betw}

@@

Although we have seen (Fig.~\ref{fig:mass-loss-comparison}) that the
mass-loss discrepancy increases with \(R_0\), it is hard to understand
why the physical size per~se might cause this.  We have therefore
looked at the correlations between all of the observed and derived
quantities, showing some of the more interesting results in
Figure~\ref{fig:correlations}.  Each row of plots shows the dependence
(\(y\) axis) of the two different derived mass-loss rates, and their
ratio, on different parameters (\(x\) axis) of the star (leftmost four
columns) and bow shell (remaining six columns).  The most significant
correlations are marked in red with the value of the Pearson
correlation coefficient, \(r\) (calculated after taking the log of all
quantities).  The values shown with dark text have \(r^2 > 0.5\),
which means that at least 50\% of the variance in the \(y\) quantity
is ``explained'' by the variance in the \(x\) quantity (although this
cannot necessarily be taken to imply causation in either direction
since it might be due to the fact that both \(x\) and \(y\) are
partially determined by a third quantity, \(z\)). For some
correlations, we also mark the linear regression slope, \(m\).  Since
we are working in logarithmic space, this is equal to the power index
in the relation \(y \propto x^m\).  Some selected weaker correlations
are also shown (fainter text).

@@

Out of the three quantities, \(R_0\), \(\ell/R_0\), and \(U\) (which
are highly correlated between themselves) we will concentrate on the
relative chord length \(\ell/R_0\) as the most likely culprit for the
discrepancy between the two mass-loss estimates.  This is because it
contains observational information that is used in the K18 method
(step K\ref{K2} of \S~\ref{app:bow-shock-data}), but is \textit{not
  used} in the \(\tau\)--\(\eta\shell\) method.  The closest
equivalent of \(\ell\) in our method is the shell thickness,
\(h\shell\), which enters in step~P\ref{P2} of
\S~\ref{sec:energy-trapp-vers}, but crucially we use a fixed fraction
of the bow radius, \(h\shell / R_0 = 0.25\), rather than basing it on
any observations.  In principle, we could derive \(h\shell\) from
\(\ell\) if we knew the radius of curvature of the shell,
\(R_{\text{c}}\), or equivalently the planitude:
\(\Pi = R_{\text{c}} / R_0\) \citep{Tarango-Yong:2018a}.  The idealized
geometry is illustrated in the inset to Figure~\ref{fig:H-versus-ell},
from which we find
\begin{equation}
  \label{eq:h-R0}
  \frac{h\shell}{R_0} = \frac{1}{8\Pi} \left(\frac{\ell}{R_0}\right)^2 \ .
\end{equation}
This is plotted in Figure~\ref{fig:H-versus-ell} for planitudes of
\(\Pi = 1.8 \pm 0.9\), which are typical of OB star bows (this will be
shown in detail in the upcoming Paper~IV).  Also shown in the figure
are the individual relative chord lengths for the K18 sources (rug
plot at top).  Although the mean value of \(\ell/R_0 \approx 1.8\)
corresponds closely to the \(h\shell/R_0 = 0.25\) that we have used,
the sources with \(\ell/R_0 < 1\) are predicted to have thinner shells
with \(h\shell/R_0 < 0.1\).  The four sources with the lowest values
of \(\ell/R_0\) are labeled on the figure (369, 339, 382, 344) and
these are precisely those sources that show the largest discrepancy
between the two mass loss methods
(Fig.~\ref{fig:mass-loss-comparison}).  Using a smaller value of
\(h\shell\) would increase \(\eta\shell\) (eq.~[\ref{eq:eta-shell}])
and hence \(\dot{M}\) (eq.~[\ref{eq:mdot-tau-eta}]), thereby reducing
the discrepancy between the two methods.

@@

K18 source~342 is the only source that shows a significant discrepancy
\textit{above} the theoretical mass-loss rate predictions.  This is
bow shock candidate~2 in a survey of mid-infrared arcs in Cygnus~X
\citep{Kobulnicky:2010a}, and is referred to as KGK2010~2 in
subsequent works.  For its early~B spectral type,
\(\dot{M} \approx \SI{3e-9}{M_\odot.yr^{-1}}\) is expected, whereas
the derived values from both mass-loss methods (panels a and b of
Fig.~\ref{fig:mass-loss-vs-luminosity}) are about 10 times larger.
This fact was already noted in K18, who suggested that the grain
emissivity models may not be appropriate for this object.  We propose
instead to investigate the idea that the shell may be predominantly
neutral instead of ionized, which might help explain other peculiar
aspects of the source.  Figure~\ref{fig:cygnus-bows} shows infrared
images of the field containing both sources~342 and 341.  The field is
located in the Cygnus~X North region, between the DR~20 and DR~21 star
forming regions, about \SI{17}{pc} north of the center of the Cygnus
OB2 association \citep[e.g.,][]{Schneider:2016a}.  It can be seen that
the two bow shocks have very contrasting morphologies and spectra.
Source~341 has a semi-circular shape, a very diffuse outer boundary,
and is only prominent between wavelengths of \SI{12}{\um} and
\SI{24}{\um}.  These characteristics are typical of many optically
thin bows seen in fully ionized gas, such as the Ney--Allen nebula
around \thD{} \citetext{compare the bow shape in Fig.~3a of
  \citealp{Smith:2005a}}, source~406 \citetext{HD~92607, which is
  ERO~36 in Carina, \citealp{Sexton:2015b}}, and the central star of
RCW~120 \citetext{not included in current samples, but see
  \citealp{Mackey:2015a, Mackey:2016a}}.  Source~342, on the other
hand, has a more parabolic shape, a sharply defined outer boundary to
its arc, and emits strongly at all wavelengths from \SI{3.6}{\um} to
\SI{150}{\um} \citetext{see also Fig.~13 of
  \citealp{Kobulnicky:2010a}}.  The parabolic arc shape and the broad
SED are both reminiscent of LP~Ori (more details on the Orion Nebula
bows will be provide in Paper~VI), and another bow that bears some
similarities is Carina's Sickle object \citetext{ERO~21
  \citealp{Sexton:2015b}, see also \citealp{Ngoumou:2013a} and \S~4 of
  \citealp{Hartigan:2015a}}.  Note also the second outer rim in this
source, which emits primarily at \SI{5.8}{\um}, \SI{7.9}{\um}, and
\SI{12}{\um}. This appears similar to the double-bow structure seen in
IRAS~03063+5735 \citep{Kobulnicky:2012a}.  Finally, it has the coldest
dust of any of the K18 sources, as determined from the mid-to-far
infrared color temperatures (\(T_{22/70} = \SI{70}{K}\),
\(T_{70/150} = \SI{69}{K}\) from Tab.~5 of
\citealp{Kobulnicky:2017a}).

If source~342 has trapped the ionization front in its shell, then
\(\eta\shell\) has been overestimated and the source should be moved
vertically down on Figure~\ref{fig:All-sources-eta-tau} in a similar
way to LP~Ori.  The exact correction factor is unknown, since it
depends on the temperature and magnetic field in the neutral shell,
but it could easily be of order 10, which would take the shell into
the radiation-supported regime.  The derived mass-loss rate would
hence be reduced from the anomalously high value of
Figure~\ref{fig:mass-loss-comparison} to essentially zero.  However,
this requires that the shell be capable of absorbing all the ionizing
photons from the central star, which implies a lower limit to the
shell optical depth: \(\tau > \tau\iftrap\), see Paper~I's
\S~3.1.\footnote{%
  Note that \(\tau\iftrap < 1\) is allowed, since \(\tau\) is the
  ultraviolet \emph{dust} optical depth of the shell, whereas it is
  the EUV \textit{gas} opacity that is most important for trapping the
  ionization front.  } %
In the radiation-supported bow wave (RBW) regime this is
\begin{equation}
  \label{eq:tau-trap-rbw}
  \text{RBW:}\quad \tau\iftrap \approx 7.1 \, \left( \frac{S_{49} \, \kappa_{600}}{L_4} \right)^{1/2} \ ,
\end{equation}
while in the wind-supported bow shock (WBS) regime it is
\begin{equation}
  \label{eq:tau-trap-wbs}
  \text{WBS:}\quad \tau\iftrap \approx 102 \, \frac{S_{49} \, \kappa_{600}}{\eta\wind\, L_4}  \ .
\end{equation}
In these equations, which are derived from equations~(8, 10, 12, 24)
of Paper~I, \(S_{49}\) is the ionizing photon luminosity of the star
in units of \SI{e49}{s^{-1}}, while \(L_4\) and \(\kappa_{600}\) are
defined in \S~\ref{sec:energy-trapp-vers} and \(\eta\wind\) in
\S~\ref{sec:mass-loss-determ}.  Within the uncertainties, the
observationally inferred spectral type of B0--B2V of source~342 is the
same as the \SI{10}{M_\odot} main-sequence star used in Papers~I
and~II, which has a ratio of ionizing to bolometric luminosity
\(S_{49}/L_4 = \num{2.1e-4}\).  Substituting into
equation~\eqref{eq:tau-trap-rbw} yields \(\tau\iftrap \approx 0.1 \)
for the RBW case, whereas the observed optical depth is more than an
order of magnitude lower: \(\tau \approx 0.005\).  Similar
difficulties arise if one assumes a wind-supported bow shock, in which
case \(\tau < \eta\wind\) by definition.  Combined with
equation~\eqref{eq:tau-trap-wbs}, this then implies a lower limit for
the wind momentum efficiency: \(\eta\wind > 0.14\).  Given that we
must always have \(\eta\shell \ge \eta\wind\)
(eq.~[\ref{eq:eta-shell-components}]), this is inconsistent with the
observed \(\eta\shell = 0.07 T_4 / \kappa_{600} h_{1/4}\), especially
since the whole point of the exercise is to reduce \(\eta\shell\) via
a reduction in \(T_4\).

Therefore, we have shown that a neutral shell is not consistent with
the observational data for source~342, and so this is unlikely to be
the explanation for the seemingly high mass loss rate.  Instead, it is
possible that the explanation is simply that the stellar luminosity
has been underestimated, since the luminosity class is not well
constrained by spectroscopy (K18).  If the star were B1~III instead of
B1~V, then the luminosity would be 4 times higher.  This could be due
to a combination of having underestimated the distance and having
underestimated the foreground extinction.  The assumed distance of
\(D= \SI{1.3}{kpc}\) comes from a study of eclipsing binaries in the
Cygnus~OB2 association \citep{Kiminki:2015a}, but GAIA~DR2 parallaxes
for the association clearly show two sub-groups at
\(D = \SI{1.76}{kpc}\) and \SI{1.35}{kpc}, with the farther group
being the dominant one \citep{Berlanas:2019a}.  The GAIA parallax for
source~342 yields a median and 90\% confidence interval of
\(1.65^{+0.18}_{-0.16} \, \si{kpc}\) (same methodology as
App.~\ref{sec:hd-53367-v750}),
% \SIrange{1.49}{1.83}{kpc}
which clearly indicates it is in the farther group.  Taking the median
distance of \SI{1.65}{kpc} would raise \(L_*\) by a factor 1.61 and
increasing the visual extinction \(A_V\) by 1 magnitude would give an
additional factor of 2.51 for a total increase by \(\approx 4\), as we
are looking for.  To find the effects on the derived quantities, we
can sum the Jacobian elements in the first two rows of
Table~\ref{tab:derived-parameters}, multiplied by the changes in
observed log quantities: \(\Delta D \approx \SI{+0.1}{dex}\) and
\(\Delta L_* \approx \SI{+0.6}{dex}\). For example:
\begin{equation}
  \label{eq:delta-derived}
  \Delta\tau = J_D(\tau)\, \Delta D + J_{L_*}(\tau)\, \Delta L_*
\end{equation}
and similarly for the other quantities.  This yields
\(\Delta \tau \approx \SI{-0.4}{dex}\),
\(\Delta \eta\shell \approx \SI{-0.9}{dex}\),
\(\Delta \dot{M} \approx \SI{-0.3}{dex}\), and
\(\Delta \dot{M}_{\text{K18}} \approx \SI{-0.1}{dex}\).  In
Figure~\ref{fig:mass-loss-vs-luminosity}a this would move source~342
substantially to the right and slightly down, thus transforming it
from an extreme outlier to an unremarkable source in the center of the
pack.  It would be disappointing if such a prosaic explanation were
the correct one, given all the other peculiarities of this source
listed in the first paragraph of this section.  However, based on
current evidence, the more interesting and exotic explanations are
less plausible.
